Does It Scale? Static Output Approximation of PHP Web Applications Using Symbolic Execution

### 2017-01-13 paper.tex
refactored 2 w/o 2.2

\section{State Of the Art}\label{sec:stateoftheart}
Symbolic execution is one of integral analysis techniques used by the tools
whose practicality we aim to evaluate. This section recaps the idea of symbolic
execution, the tools which make use of it, and both conceptual and
language-related limitations.

\subsection{Symbolic Execution}
Symbolic execution is a static analysis technique that was proposed by James C.
King in 1976 \cite{King1976}. Symbolic execution allows to explore all feasible
paths in a program. Based on normal program execution, the execution semantics
is extended to handle symbolic values, which are abstract, but fixed; an
execution becomes symbolic by introducing symbolic values as program inputs
instead of concrete values \cite{King1976,Darringer1978}. These symbolic values
are then propagated and used throughout the execution.

Execution starts with a plain path condition, usually a tautology. Whenever the
control-flow can be split into different branches, the corresponding path
conditions (guards for instance) are conjoined with the previous path condition
\cite{King1976}. Additionally, the conjoined path condition can be checked for
satisfiability to exclude infeasible paths. Consequently, for a given program
symbolic execution computes a mapping from (symbolic) input values to output values.

@@

\subsection{Existing Tool Support for PHP}\label{sec:existing_tools}
All tools proposed so far leverage a representation of all possible HTML client
page output. Since any variant can be analyzed in particular, this enables tool
support addressing the web application as a whole in spite of its staged
nature, where parts of the web application (client-side output) are generated
dynamically.

Based on the approximated output representation subsequent analyses can be
conducted, which have been implemented in the following tools:
\begin{itemize}
	\item {\emph{PhpSync}: Using all variants of  HTML client page output, every
	single one can be statically checked for Markup Validity, i.e., if the web page
	conforms to syntactical specifications for HTML and other client-side
	languages. After validation errors are detected, auto-fixes are provided.
	Otherwise, the validation error can be traced back to source code responsible
	for the defect, which then can be refactored manually
	\cite{Nguyen:2011:AFH:2190078.2190142}. }

@@

\subsection{Assumptions And Limitations}\label{sec:limitations}
In addition to the limitations introduced by  symbolic execution, such as
symbolic inputs and one-time loop execution, the symbolic execution described
in \cite{Nguyen:2014:BCG:2635868.2635928} does not support advanced language
features, including object-oriented programming. Moreover, the range of
standard library functions supported are mostly string operations, yet PHP
provides a large collection of functions for array operations.
All three tools described in Section \ref{sec:existing_tools} though have only
been applied to systems that are small and not maintained any more. Despite the
functional benefits these tools provide to developers, their practicality for
large and modern systems with respect to advanced language support has not been
evaluated.

>>>>

\section{State Of the Art}\label{sec:stateoftheart}
Symbolic execution is an analysis techniques used by the tools
whose practicality we aim to evaluate. This section recaps the idea of symbolic
execution, the tools which make use of it, and both conceptual and
language-related limitations.

\subsection{Symbolic Execution}
Symbolic execution is a static analysis technique that was proposed by James C.
King in 1976 \cite{King1976}. Symbolic execution allows to explore feasible
paths in a program. Based on normal program execution, the execution semantics
is extended to handle symbolic values. An execution becomes symbolic by
assuming symbolic values as program inputs rather than obtaining concrete
values \cite{King1976,Darringer1978}. These symbolic values are then propagated
and used throughout the execution.

Execution starts with a tautology path
condition. The control-flow can be split whenever the decision between branches
is ambiguous. This is the case, when conditional expressions, for example for
if-statements, evaluate to a symbolic value rather than an actual result.
The corresponding path conditions (guards for instance) are conjoined with the
previous path condition \cite{King1976}. Additionally, the conjoined path
condition can be checked for satisfiability in order to exclude infeasible
paths.

@@

\subsection{Existing Tool Support for PHP}\label{sec:existing_tools}
All tools proposed so far leverage a representation of all possible HTML client
page output. Since any single client page output variant can be analyzed this
enables tool support addressing the web application as a whole in spite of its
staged nature, where parts of the web application are
generated dynamically.
Based on the approximated output representation, subsequent analyses can be
conducted:
\begin{itemize}
	\item \emph{PhpSync}: Using all variants of  HTML client page output, every
	single one can be statically checked for markup validity, i.e., if the web page
	conforms to syntactical specifications for HTML and other client-side
	languages. After the tool detects validation errors, auto-fixes
	can be provided. Otherwise, it traces validation errors back to
	source code responsible for the defect, which then can be refactored manually
	\cite{Nguyen:2011:AFH:2190078.2190142}.

@@

\subsection{Assumptions And Limitations}\label{sec:limitations}
In addition to the assumptions introduced by symbolic execution, such as
symbolic inputs and one-time loop execution, the symbolic execution
engine described in previous work \cite{Nguyen:2014:BCG:2635868.2635928} does
not support advanced language features, including object-oriented programming. Moreover, the range of
standard library functions supported are mostly string operations, yet PHP
provides a large collection of functions for array operations.
All three analyses described in Section \ref{sec:existing_tools} though have
only been applied to systems that are small and not maintained any more. Despite the
functional benefits these tools provide to developers, their practicality for
large and modern systems with respect to advanced language support has not been
evaluated.
